%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}

\vspace{-2mm}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  
\cventry
  {Master of Science in Computer Science} % Degree
  {Tsinghua University} % Institution
  {Beijing, China} % Location
  {Sep. 2019 - June 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) bullet points
      \item {GPA: 3.65/4.0.}
      \item {Built a Rust interpreter, NFD2Rust, for NFD, a domain-specific language for cross-platform network functions within two months. 
      Interpreting a Cpp-like language (NFD) to Rust executable, requiring plenty of additional optimization to satisfy Rust syntax rules, including lifetimes and ownerships.
      }
      \item{Maintained 8 servers connecting with both programmable and commodity switches in a server room, including setting up Ethernet connections and configurations, gatekeepers between intranet and internet, 
      and reverse proxy for access to private servers.
      }
      \item{Cooperated with Hwawei engineers on a collaborative design of network gateways between network switches and servers. Offloaded most elephant flows, 
      at most 83\% traffic, to high-throughput switches by traffic prediction.}
      \item{Courses Taken:}
      \begin{itemize}
        \item{Formal Methods and Protocol Engineering in Computer Network.} Following my previous research during my Bachelor's degree on applying formal 
        verification on smart contracts. Systematically learned verification tools such as PITSv3 and apply them to my master's research on custom protocols.
        \item{Distributed System.} Implemented the Raft consensus algorithm to provide a fault-tolerant key/value service as the first project in Golang.
        \item{Network Security.} Experimented with applying up-to-date protocols (e.g., ESNI on DNS) on different websites to achieve censorship evasion 
        in mainland China.
        \item{Computer System Performance Testing.} Motivated by my previous working experience on tracing code in the QEMU project with a huge code base.
        Systemically learned different evaluation approaches including instrumentation or profiling tools like gprof.
			\end{itemize}
    \end{cvitems}
  }

  \vspace{-3mm}

  \cventry
    {Bachelor of Engineering in Electrical Engineering} % Degree
    {National Cheng Kung University} % Institution
    {Tainan, Taiwan} % Location
    {Sep. 2015 - June 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{GPA: 3.64/4.3.}
        \item {Persistently contributed to writing the book expected to be released this year, "Demystifying the Linux CPU Scheduler", with professors and undergraduate students. Elaborate on 
        evaluating scheduler designs like CFS and corresponding implementations.
        }
        \item{Engaged in open-source communities abroad including making presentations at FOSSASIA and HKOSCon.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
