%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}

\vspace{-2mm}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {} % Affiliation/role
    {Conference Paper} % Organization/group
    {} % Location
    {} % Date(s)
    {
      \vspace{-2mm}
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {\textbf{Chen, Y.}, Wu, W., Shen, S.H. and Zhang, Y., 2022, June. "NQ/ATP: Architectural Support for Massive Aggregate Queries in Data Center Networks." 
        In \emph{2022 IEEE/ACM 30th International Symposium on Quality of Service (IWQoS)} (pp. 1-10). IEEE.
        }
        \begin{itemize}
          \item {Resolved incast bandwidth bottlenecks in scaling data-center networks by traffic aggregation through programmable switches.}
          \item {Reduced 96.82\% link usage even with dynamic routing, performance boosts even further as the network size scales.}
        \end{itemize}
        \item {Lao, C., Le, Y., Mahajan, K., \textbf{Chen, Y.}, Wu, W., Akella, A. and Swift, M.M., 2021, April. "ATP: In-network Aggregation for Multi-tenant Learning." 
        In \emph{NSDI} (Vol. 21, pp. 741-761).
        }
        \begin{itemize}
          \item{Mitigated incast traffic towards parameter servers distributed machine learning with multiple tenants sharing the limited memory space on switches.}
          \item {Guaranteed performance and correctness with multiple tenants competing for limited memory usage.}
          \item {Accerlated training processes ranging from 1.24 to 8.7 with different models. \textbf{Best Paper Award}.}
        \end{itemize}
      \end{cvitems}
    }
  \vspace{-2mm}

%---------------------------------------------------------
\cventry
{} % Affiliation/role
{Open-source Conference Sessions} % Organization/group
{} % Location
{} % Date(s)
{
  \vspace{-2mm}
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {Chen, Y., 2022, July. "Why should we attend conferences oversea ? (translated from Mandarin)." Tapei.
    In \emph{COSCUP}.
    }
    \item {Chen, Y., 2019, June. "Formal Verification on Smart Contract." Hong Kong.
    In \emph{HKOSCon}.
    }
    \item {Chen, Y., 2018, March. "Only Empty Lip Service ? Free Software Development in Taiwan." Singapore.
    In \emph{FOSSASIA}.
    }
  \end{cvitems}
}
\vspace{-2mm}  

\end{cventries}
